% For another similar setup, see resume.tex
\formatcoversections
\begin{minipage}{\dimexpr0.5\linewidth-0.5\columnsep\relax}
  \invisiblepart{Cover letter}
  \input{sections/about.tex}
\end{minipage}

\setlength{\parskip}{\baselineskip} % Leave a line between paragraphs

Dear Hiring Manager,

I am \textbf{Dhruv Bhanushali}, and this is my application for a full-time role
as a \textbf{software engineer}. Let me go over the reasons why I believe I am a
perfect fit for the role, and why the role is a perfect fit for me.

\coversection{Why me?}

\begin{itemize}[nosep, parsep = 1mm, leftmargin = *]
  \item \textbf{I am tenacious.} I started web development at IIT Roorkee during
  my bachelors' as a hobby. Four years of practice later, I was the Chief
  Technology Coordinator of
  \href{https://https://internet.channeli.in/maintainer_site/}{Information
  Management Group}, mentoring a fifty-strong group of developers and designers.

  \item \textbf{I go the extra mile.} I took up the task of addressing
  shortcomings in the intranet portal of the institute. Finding major flaws in
  the core assumptions, I single-handedly re-wrote
  \href{https://omniport.readthedocs.io}{Omniport}, over the course of a year,
  on a modernised Docker/Django/React stack.

  \item \textbf{I thrive on challenges.} Scaling a portal hosted on humble
  hardware to serve over 200k requests a day from over 10k users, including
  students, faculty and administration, was one of my significant achievements
  in college.

  \item \textbf{I pursue perfection.} I put my heart and soul into each project
  I undertake. For Omniport, I designed the scalable
  \href{https://github.com/IMGIITRoorkee/omniport-docker/}{architecture},
  developed the modular
  \href{https://github.com/IMGIITRoorkee/omniport-backend/}{backend}, integrated
  the frontend and wrote comprehensive documentation for all future
  contributors.

  \item \textbf{I am a fast learner.} I learned Sphinx to write the
  \href{https://github.com/IMGIITRoorkee/omniport-docs/}{best documentation} for
  Omniport, \prettylatex{} to build
  \href{https://github.com/dhruvkb/resume/}{my résumé} and this cover letter,
  and finally Sass and Vue for Vocabulary. Then mastered the last
  two to power my \href{https://dhruvkb.github.io/}{personal website}.

  \item \textbf{I pride myself on code quality.} I make it a point to write
  test-driven, self-documenting code. Though I probably am the only person who
  would ever see the 
  \href{https://github.com/dhruvkb/portfolio/}{source code}
  of my portfolio or the \prettylatex behind
  \href{https://github.com/dhruvkb/resume/}{my résumé}
  and cover letter, both are completely documented.

  \item \textbf{I am an ardent advocate of open source.} I designed Omniport's
  score to be decoupled from the institute specifics so that the project could
  benefit other institutions. As an alumnus, I still review PRs made to Omniport
  and help new contributors get started.
\end{itemize}

I would request you to please take a moment to review my résumé, which follows
this page. I genuinely believe I have the dedication, skills and experience
needed not only to get the job done but also done well. If any more information
is required of me, I'll be happy to provide it. I would be thrilled if I got to
further my career with your organisation.

Thank you for considering my application and reading through this verbose cover
letter!

Looking forward to hearing from you,

Regards,\\
Dhruv Bhanushali
\setlength{\parskip}{0mm} % Leave no space between paragraphs

\vfill
\textcolor{secondary}{( ˇ ▽ ˇ )/}
\pagebreak