\begin{multicols}{2}[]
  \input{sections/about.tex}
  \columnbreak  
  \\
\end{multicols}

\setlength{\parskip}{\baselineskip} % Leave a line between paragraphs
\vspace{-0.5cm}
Dear Creative Commons team,

I am \textbf{Dhruv Bhanushali}, and this is my application for a full-time role
at Creative Commons as a \textbf{Frontend engineer}. Let me go over the reasons
why I believe I am a perfect fit for the role, and why the role is a perfect fit
for me.

\textcolor{green}{Why me?}
\begin{itemize}[nosep, parsep=1mm, leftmargin=*]
  \item \textbf{I am tenacious.} I started web development at IIT Roorkee during
  my bachelors' as a hobby. Four years of practice later, I was the Chief
  Technology Coordinator of
  \href{https://https://internet.channeli.in/maintainer_site/}{Information
  Management Group}, mentoring a fifty-strong group of developers and designers.

  \item \textbf{I go the extra mile.} I took up the task of addressing
  shortcomings in the intranet portal of the institute. Finding major flaws in
  the core assumptions, I single-handedly re-wrote
  \href{https://omniport.readthedocs.io}{Omniport}, over the course of a year,
  on a modernised Docker/Django/React stack.

  \item \textbf{I thrive on challenges.} Scaling a portal hosted on humble
  hardware to serve over 200k requests a day from over 10k users, including
  students, faculty and administration, was one of my significant achievements
  in college.

  \item \textbf{I pursue perfection.} I put my heart and soul into each project
  I undertake. For Omniport, I designed the scalable
  \href{https://github.com/IMGIITRoorkee/omniport-docker/}{architecture},
  developed the modular
  \href{https://github.com/IMGIITRoorkee/omniport-backend/}{backend}, integrated
  the frontend and wrote comprehensive documentation for all future
  contributors.

  \item \textbf{I am a fast learner.} I learned Sphinx to write the
  \href{https://github.com/IMGIITRoorkee/omniport-docs/}{best documentation} for
  Omniport, {\fontfamily{lmr}\selectfont\LaTeX} to build
  \href{https://github.com/dhruvkb/resume/}{my resume} and this cover letter,
  and finally Stylus, Sass and Vue.js for Vocabulary. Then mastered the last
  three to power my \href{https://dhruvkb.github.io/}{personal website}.

  \item \textbf{I pride myself on code quality.} I make it a point to write
  test-driven, self-documenting code. Though I probably am the only person who
  would ever see the \href{https://github.com/dhruvkb/portfolio/}{source code}
  of my portfolio or the
  \href{https://github.com/dhruvkb/resume/}{\fontfamily{lmr}\selectfont\LaTeX}
  behind my resume, both are completely documented.

  \item \textbf{I am an ardent advocate of open source.} I designed Omniport's
  core to be decoupled from the institute specifics so that the project could
  benefit other institutions. As an alumnus, I still review PRs made to Omniport
  and help new contributors get started.
\end{itemize}

\textcolor{green}{Why Frontend engineer @ CC?} 
\begin{itemize}[nosep, parsep=1mm, leftmargin=*]
  \item \textbf{Steadfast mentorship.} Thanks to the mentorship from Hugo Solar,
  Vocabulary which was formerly my independent proposal for GSoC '19, became a
  reality after months of efforts with over 300 commits and over 17 alpha
  releases.

  \item \textbf{Community involvement.} I have become so deeply involved with
  the sub-community that has sprung up around Vocabulary, that to stay in the
  loop, I went on to work four additional contracts and also mentored for
  Outreachy twice.

  \item \textbf{Constant learning.} Every task I've taken up at CC has presented
  opportunities to learn things I would never have explored otherwise. I am
  fortunate to have learned so much from the CC team, from PR reviews to the
  research involved in the task.

  \item \textbf{Welcoming team.} I'm grateful to the CC team for providing me
  with a chance to be a part of something bigger than myself and to participate
  in their product sync-ups, engineering meetings and even game-nights!

  \item \textbf{Opportunity for impact.} As a developer, I immensely value the
  opportunity to make a positive impact on the lives of end users or other
  developers. CC products, with their far reach and diverse userbase, provide
  ample number of such opportunities.
\end{itemize}

\textcolor{green}{Why me for Frontend engineer @ CC?}
\raggedright\begin{itemize}[nosep, parsep=1mm, leftmargin=*]
  \item \textbf{The position would come as a natural transition for me.} Because
  I am performing quite a few of the primary responsibilities even today, such
  as improving and mentoring the integration of Vocabulary, I can start
  generating value immediately.

  \item \textbf{I have contributed to CC Search before.} During the application
  period before GSoC, I was solving bugs and implementing features in both the
  backend and frontend of CC Search. During this period, I collaborated with
  Breno Ferreira and Alden Page.

  \item \textbf{I'm one of the founding members of Vocabulary.} I've not only
  seen but instead played a part in the evolution of the project over time. I've
  seen the code, and the community around it, evolve, grow and take on a life of
  its own.

  \item \textbf{I have experience in working remotely.} Having worked with CC
  remotely for over a year, from the very first GSoC to the very recent
  mentorship, I have become familiar with the ways of working (and making
  friends) in a remote environment.

  \item \textbf{I can bring diverse perspectives to the table.} I am proficient
  in many aspects of web development from Python backends to Vue.js frontends to
  the Dockerised deployments. To some extent, I can also provide feedback in
  terms of UI/UX.

  \item \textbf{I have positive references from the CC team.} Both Hugo Solar
  and Breno Ferreira, who have mentored me in the past, will surely have some
  \href{https://www.linkedin.com/in/dhruvkb/}{positive testimonials} and vouch
  for me.
\end{itemize}

I would request you to please take a moment to review my résumé, which follows
this page. I genuinely believe I have the dedication, skills and experience
needed not only to get the job done but also done well. If any more information
is required of me, I'll be happy to provide it. I have been looking forward to
an opportunity like this for many months and would be thrilled if I got to
continue my journey with CC on a deeper level.

Thank you for considering my application and reading through this verbose cover
letter!

Looking forward to hearing from you,

Regards,\\
Dhruv Bhanushali
\setlength{\parskip}{0cm} % Leave no space between paragraphs

\pagebreak