%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resumesection{Experience}{Experience}{\iconBriefcase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\experiencesubsection%
{Software @ Creative Commons}% Label
{Software engineer}% Role
{\href{https://creativecommons.org/}{Creative Commons}}% Organisation
{April 2019 -- Present}% Time period
{Google Summer of Code}% Attribute#2
{\iconGoogle}% Icon#2

\sectiondescription{
  \begin{itemize}[nosep, leftmargin=*]
    \item Developed the Vocabulary design system and Vue.js bindings.
    \item Collaborated in decision-making with design and dev team.
    \item Identified areas of improvement and spearheaded changes.
    \item Nurtured an active developer community around the project.
    \item Initiated and helped Vocabulary integration with CC sites.
    \item Pushed features and patches to back \& front end of CC Seach.
  \end{itemize}
}

\experiencesubsection%
{Outreachy mentor @ Creative Commons}% Label
{Outreachy mentor}% Role
{\href{https://creativecommons.org/}{Creative Commons}}% Organisation
{November, 2019 -- March, 2020}% Time period
{Remote}% Attribute#2
{\iconHome}% Icon#2

\sectiondescription{
  \begin{itemize}[nosep, leftmargin=*]
    \item Triaged issues and reviewed PRs during application period.
    \item Helped new contributors identify easier issues to get started.
    \item Offered code help on Slack and reviewed draft proposals.
    \item Guided my mentee to gain first-hand FOSS work-experience.
  \end{itemize}
}

\onsiteexperiencesubsection%
{Infrastructure @ HackerEarth}% Label
{Infrastructure engineer (intern)}% Role
{\href{https://hackerearth.com/}{HackerEarth}}% Organisation
{May -- July, 2018}% Time period
{Bengaluru, India}% Location

\sectiondescription{
  \begin{itemize}[nosep, leftmargin=*]
    \item Wrote the IaC for the entire production architecture.
    \item Wrote tooling to deploy the IaC in an alternate AWS AZ.
    \item Wrapped Boto3 in a Python + Django web-environment.
    \item Developed an EC2 instance launch and termination engine.
    \item Isolated staging and production in separate VPCs.
    \item Enabled deployment of new staging VPCs in one click.
  \end{itemize}
}

\onsiteexperiencesubsection%
{Software @ HackerEarth}% Label
{Software engineer (intern)}% Role
{\href{https://hackerearth.com/}{HackerEarth}}% Organisation
{May -- July, 2017}% Time period
{Bengaluru, India}% Location

\sectiondescription{
  \begin{itemize}[nosep, leftmargin=*]
    \item Wrote a code-evaluation engine to evaluate Java projects.
    \item Wrote tooling to automatically build and execute projects.
    \item Wrapped Ant in an async message-based Python evaluator.
    \item Developed the scaffolding architecture using RabbitMQ.
    \item Added provider-agnostic database connectivity using JDBC.
    \item Installed security policies such as memory and I/O limits.
  \end{itemize}
}

\experiencesubsection%
{CTC @ IMG}% Label
{Chief technology coordinator}% Role
{\href{https://img.channeli.in/}{Information Management Group}}% Organisation
{2016 -- 2019}% Time period
{IIT Roorkee}% Attribute#2
{\iconInstitute}% Icon#2

\sectiondescription{
  Information Management Group (IMG) is the student body that developed, manages
  and upgrades both the content management system powering the IIT Roorkee
  website and Channel~i, the official intranet portal.
  \begin{itemize}[nosep, leftmargin=*]
    \item Pivoted IMG as a group from app to platform development.
    \item Replaced Channel~i, and its suite of apps, with Omniport.
    \item Piloted a complete upgrade of the stack and technology.
    \item Mentored a team of over 50 developers and designers.
    \item Halved timelines by replacing the development paradigm.
    \item Containerised and isolated the development process.
    \item Fostered OSS culture with a record 30 repos open-sourced.
    \item Lead IMG to 10 and 13 GSoC selections in 2018 and 2019.
    \item Reinvigorated IMG's popular image on social media.
  \end{itemize}
}