%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colouredsection{Internships}{Internships}{cyan}{\fasBriefcase}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\datedsubsection{Software @ Creative Commons}% Keyword
{Software developer}% Role
{\href{https://creativecommons.org/}{Creative Commons}}% Organisation
{April -- September, 2019}% Time period
{Google Summer of Code}% Location

\sectiondescription{
  \begin{itemize}[nosep, leftmargin=*]
    \item Developed Vocabulary, a cohesive design system.
    \item Revamped the UI of CC Search, powered by Vocabulary.
    \item Initiated Vocabulary integration into other CC projects.
    \item Contributed features and patches to the CC Catalog API.
  \end{itemize}
}

\onsiteexperiencesubsection{Infrastructure @ HackerEarth}% Keyword
{Infrastructure engineer}% Role
{\href{https://hackerearth.com/}{HackerEarth}}% Organisation
{May -- July, 2018}% Time period
{Bengaluru, India}% Location

\sectiondescription{
  \begin{itemize}[nosep, leftmargin=*]
    \item Wrote the IaC for the entire production architecture.
    \item Wrote tooling to deploy the IaC in an alternate AWS AZ.
    \item Wrapped Boto3 in a Python + Django web-environment.
    \item Developed an EC2 instance launch and termination engine.
    \item Isolated staging and production in separate VPCs.
    \item Enabled deployment of new staging VPCs in one click.
  \end{itemize}
}

\onsiteexperiencesubsection{Software @ HackerEarth}% Keyword
{Software developer}% Role
{\href{https://hackerearth.com/}{HackerEarth}}% Organisation
{May -- July, 2017}% Time period
{Bengaluru, India}% Location

\sectiondescription{
  \begin{itemize}[nosep, leftmargin=*]
    \item Wrote a code-evaluation engine to evaluate Java projects.
    \item Wrote tooling to automatically build and execute projects.
    \item Wrapped Ant in an async message-based Python evaluator.
    \item Developed the scaffolding architecture using RabbitMQ.
    \item Added provider-agnostic database connectivity using JDBC.
    \item Installed security policies such as memory and I/O limits.
  \end{itemize}
}