%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resumesection{Open source}{Open source}{\iconLockOpen}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\worksubsection%
{Vocabulary}% Label
{\href{https://creativecommons.github.io/cc-vocabulary/}{Vocabulary}}% Title
{Design system}% Category
{May 2019 -- Present}% Time period
{Sass; Vue.js; Storybook}% Tech stack

\sectiondescription{
  Vocabulary is a cohesive design system, and Vue.js components implementing it,
  to unite the web facing \iconCreativeCommons~Creative~Commons.
  \begin{itemize}[nosep, leftmargin=*]
    \item Planned the code locations and repository structure.
    \item Developed Sass styles and corresponding Vue.js components.
    \item Integrated the documentation with an interactive Storybook.
    \item Setup visual regression tests and CI/ CD for \href{https://cc-vocabulary.netlify.com}{docs} and \href{https://www.npmjs.com/package/@creativecommons/vocabulary}{builds}.
    \item Synchronized coded components with Figma requirements.
  \end{itemize}
}


\worksubsection%
{Omniport backend}% Label
{\href{https://github.com/IMGIITRoorkee/omniport-backend/}{Omniport backend}}% Title
{Campus portal platform}% Category
{March 2018 -- Present}% Time period
{Django; React}% Tech stack

\sectiondescription{
  Omniport is a platform for institutes to deploy their web portal (like 
  Channel~i by IMG for IIT-R), by and for the students.
  \begin{itemize}[nosep, leftmargin=*]
    \item Planned it to be unopinionated to suit any institute's needs.
    \item Developed Omniport to be generic but customisable.
    \item Developed extension capability with plug-and-play apps.
    \item Developed latest features such as HTTP/2 and WebSockets.
    \item Added OAuth2 provider functionality for 3rd-party auth.
    \item Launched as a mobile responsive progressive web app.
    \item Composed the Django backend, all core apps and services.
    \item Integrated with the React frontend and deployed on Docker.
  \end{itemize}
}

\ifdocoriented
\worksubsection%
{Omniport documentation}% Label
{\href{https://omniport.readthedocs.io/}{Omniport documentation}}% Title
{Holistic documentation}% Category
{March 2018 -- Present}% Time period
{Sphinx}% Tech stack

\sectiondescription{
  Omniport is a platform for institutes to deploy their web portal (like 
  Channel~i by IMG for IIT-R), by and for the students.
  \begin{itemize}[nosep, leftmargin=*]
    \item Penned the philosophy and ideals of the project.
    \item Documented the architecture, frontend and backend.
    \item Wrote helpful tutorials, how-to guides and FAQ. 
    \item Wrote in-depth reference material for functions and utils.
    \item Deployed an always up-to-date version on ReadTheDocs.
    \item Open-sourced and licensed docs under the GNU FDL.
    \item Documented the entire codebase using PyDoc and JSDoc.
  \end{itemize}
}
\else
\worksubsection%
{Omniport infrastructure}% Label
{\href{https://github.com/IMGIITRoorkee/omniport-docker/}{Omniport infrastructure}}% Title
{Container deployment}% Category
{March 2018 -- Present}% Time period
{Docker (+Compose); Bash}% Tech stack

\sectiondescription{
  Omniport is a platform for institutes to deploy their web portal (like 
  Channel~i by IMG for IIT-R), by and for the students.
  \begin{itemize}[nosep, leftmargin=*]
    \item Replaced old monolithic architecture with microservices.
    \item Containerised core and scaffolding services with Docker.
    \item Planned the infrastructure to be elastic and cloud native.
    \item Automated scaling, redundancy and reproducibility.
    \item Bash scripted image and container creation and tear-down.
    \item Deployed proofs-of-concept in dev and prod environments.
  \end{itemize}
}
\fi