%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\colouredsection{Positions of responsibility}{Positions of responsibility}{cyan}{\fasUserTie}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\onsiteexperiencesubsection{CTC @ IMG}% Keyword
{Chief technology coordinator}% Role
{\href{https://img.channeli.in/}{Information Management Group}}% Organisation
{2016 -- 2019}% Time period
{IIT Roorkee}% Location

\sectiondescription{
  Information Management Group (IMG) is the student body that developed, manages
  and upgrades both the content management system, powering the IIT Roorkee
  website and Channel~i, the official intranet portal.
  \begin{itemize}[nosep, leftmargin=*]
    \item Pivoted IMG as a group from app to platform development.
    \item Replaced Channel~i, and its suite of apps, with Omniport.
    \item Piloted a complete upgrade of the stack and technology.
    \item Mentored a team of over 50 developers and designers.
    \item Halved timelines by replacing the development paradigm.
    \item Containerised and isolated the development process.
    \item Developed a culture of open-sourcing projects at IMG.
    \item Set the institute record of 30 repos open-sourced in a day.
    \item Lead IMG to  10 and 13 GSoC selections in 2018 and 2019.
    \item Reinvigorated IMG's popular image, utilising hitherto
          untapped social platforms such as Medium and Instagram.
  \end{itemize}
}